Parallel Global Search Algorithm with Local Tuning\\ for Solving Mixed-Integer Global Optimization Problems

### 2021-02-18 2021/Lobachevskii_BarkalovLebedev/ljmsamp.tex
Revert "Поправил формулу и заменил русскую букву"
This reverts commit 218dd72cad16e06e5218888f466113f34057398d.

\begin{enumerate}
\item 
Renumber the points $x^1,...,x^k$ of the previous trials with subscripts in ascending order of coordinate values
\begin{equation}\label{Eq:17}
0=x_0<x_1<...<x_i<...<x_k<x_{k+1}=1,
\end{equation}
and assign $z_i=g_\nu(y(x_i))$, $\nu=\nu(x_i)$, $1 \leq i \leq k$; points $x_0=0$ and $x_{k+1}=1$ are introduced additionally, values $z_0$ and $z_{k+1}$ are not set.
\item
Classify indexes  $i,1\leq i \leq k$, of the trial points from  (\ref{Eq:17}) by the number of constraints that are met at these points by constructing the sets
\begin{equation}\label{Eq:18}
I_\nu = \left\{i: 1 \leq i \leq k,\ \nu = \nu(x_i)\right\},\ 1 \leq \nu \leq m+1,
\end{equation}
containing the indices of all points $x_i,1\leq i \leq k$, with indices equal to the same value $\nu$. The boundary points $x_0=0$ and $x_{k+1}=1$ are interpreted as having zero indices, and an additional set $I_0={0,k+1}$ is assigned to them.

@@

The problems generated in our experiments had 5 discrete and 4 continuous parameters 
	\begin{eqnarray*}
	& y\in D = \left\{ -1 \leq y_j\leq 1, 1\leq j \leq 4 \right\} \subset R^4, \\
	& u\in U = \left\{ u_j \in  \left\{-1, -1/3, 1/3, 1 \right\}, 1\leq j \leq 4 \right\}.
	\end{eqnarray*}

>>>>

\begin{enumerate}
\item 
Renumber the points $x^1,...,x^k$ of the previous trials with subscripts in ascending order of coordinate values
\begin{equation}\label{Eq:17}
0=x_0<x_1<...<x_i<...<x_k<x_{k+1}=1,
\end{equation}
and assign $z_i=g_\nu(y(x_i))$, $\nu=\nu(x_i)$, $1 \leq i \leq k$; points $x_0=0$ and $x_{k+1}=1$ are introduced additionally, values $z_0$ и $z_{k+1}$ are not set.
\item
Classify indexes  $i,1\leq i \leq k$, of the trial points from  (\ref{Eq:17}) by the number of constraints that are met at these points by constructing the sets
\begin{equation}\label{Eq:18}
I_\nu = \left\{i: 1 \leq i \leq k,\ \nu = \nu(x_i)\right\},\ 1 \leq \nu \leq m+1,
\end{equation}
containing the indices of all points $x_i,1\leq i \leq k$, with indices equal to the same value $\nu$. The boundary points $x_0=0$ and $x_{k+1}=1$ are interpreted as having zero indices, and an additional set $I_0={0,k+1}$ is assigned to them.

@@

The problems generated in our experiments had 5 discrete and 4 continuous parameters 
	\begin{eqnarray*}
	& y\in D = \left\{ -1 \leq y_j\leq 1, 1\leq j \leq 4 \right\} \subset R^4, \\
	& u\in U = \left\{ u_j \in  \left\{-1, -1/3, 0, 1/3, 1 \right\}, 1\leq j \leq 5 \right\}.
	\end{eqnarray*}
